Carrier phase and amplitude estimation of $M$-ary phase shift keying using pilots and data

### 2012-05-20 paper.tex
further small edits

\begin{theorem}\label{thm:normality} (Asymptotic normality)
Under the same conditions as Theorem~\ref{thm:consistency}, let $f(r,\phi)$ be the joint probability density function of $R_1$ and $\Phi_1$, and let
\[
g(\phi) = \int_{0}^{\infty} r f(r,\phi) dr.
\]
Put $\hat{\lambda}_L = \sfracpart{\theta_0 - \hat{\theta}}_\pi$ and $\hat{m}_L = \hat{\rho} - \rho_0 G(0)$. If $g(\phi)$ is continuous at $\phi = (2k+1)\tfrac{\pi}{M}$ for each $k = 0, 1, \dots M-1$, then the distribution of $(\sqrt{L}\lambda_L, \sqrt{L}m_L)$ converges to the bivariate normal with zero mean and covariance
\[
C = \frac{1}{(p + H d)^2} \left( \begin{array}{cc} 
pA_1 + dA_2 & ? \\
? & ?
\end{array} \right)
\]
as $L \rightarrow \infty$, where
\[
H = h_2(0) -  2 \sin(\tfrac{\pi}{M}) \sum_{k = 0}^{M-1} g(\tfrac{(2k+1)\pi}{M}),
\]
\[
A_1 = \expect R_1^2\sin^2(\Phi_1), \qquad A_2 = \expect R_1^2\sin^2\fracpart{\Phi_1}.
\]
\end{theorem}

@@

\begin{lemma}\label{lem:expRvlamphi}
$W(\lambda) =  \lambda(H_1 + \gamma(\lambda))$ where $\gamma(\lambda)$ is a function that goes to zero as $\lambda$ goes to zero.
\end{lemma}
\begin{IEEEproof}
In this lemma, as Lemma~\ref{lem:k2conv}, we are working under the assumption that that $0 \leq \lambda < \frac{\pi}{M}$.  An analgous argument follows when $-\tfrac{\pi}{M} \leq \lambda < 0$.  Recalling that $f(r,\phi)$ is the joint probability density function of $R_1$ and $\Phi_1$, then,
\begin{align*}
W(\lambda) &= \expect R_1 v(\lambda, \Phi_1) = \int_0^{2\pi}\int_{0}^\infty r v(\lambda, \phi) f(r,\phi) dr d\phi \\
&= \int_0^{2\pi} v(\lambda, \phi) g(\phi) d\phi,
\end{align*}
and, since $v(\lambda, \phi) = \sum_{k\in\ints} v_k(\lambda, \phi)$,
\begin{equation}\label{eq:Winfsum}
W(\lambda) = \sum_{k \in \ints} \int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi.
\end{equation}
Now, when $0 < k < M$, we have $0 < \psi_{k-1} < \psi_k < 2\pi$, so, using~\eqref{eq:vk},
\begin{align*}
\int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi &= \int_{\psi_{k-1}}^{\psi_{k}} v_k(\lambda, \phi) g(\phi) d\phi \\
&= \int_{\psi_{k} - \lambda}^{\psi_{k}} (s_k(\phi) + \lambda\eta_k(\lambda, \phi)) g(\phi) d\phi \\
&\hspace{1cm} +  \int_{\psi_{k-1}}^{\psi_{k} - \lambda}\lambda\zeta_k(\lambda)g(\phi) d\phi.
\end{align*}
When $k = 0$, we have $\psi_{k-1} < 0 < \psi_k - \lambda < \psi_k < 2\pi$, so that
\begin{align*}
\int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi &= \int_{0}^{\psi_{k}} v_k(\lambda, \phi) g(\phi) d\phi \\
&= \int_{\psi_{k} - \lambda}^{\psi_{k}} (s_k(\phi) + \lambda\eta_k(\lambda, \phi)) g(\phi) d\phi \\
&\hspace{1cm} +  \int_{0}^{\psi_{k} - \lambda}\lambda\zeta_k(\lambda)g(\phi) d\phi ,
\end{align*}
and when $k = M-1$, we have $0 < \psi_{k-1} < 2\pi < \psi_k - \lambda$, so that
\begin{align*}
\int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi &= \int_{\psi_{k-1}}^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi \\
&= \int_{\psi_{k-1}}^{2\pi}\lambda\zeta_k(\lambda)g(\phi) d\phi.
\end{align*}
Otherwise, when $k < 0$ or $k > M$, 
\[
\int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi = 0
\]
So the infinite sum in~\eqref{eq:Winfsum} is actually a finite sum,
\begin{align*}
W(\lambda) &= \sum_{k=0}^{M} v_k(\lambda, \phi) g(\phi) d\phi \\
&= \sum_{k=0}^{M-1}\int_{\psi_{k} - \lambda}^{\psi_{k}} (s_k(\phi) + \lambda\eta_k(\lambda, \phi)) g(\phi) d\phi \\
&\hspace{0.5cm} + \sum_{k=0}^{M-1} \int_{\psi_{k-1}}^{\psi_{k} - \lambda}\lambda\zeta_k(\lambda)g(\phi) d\phi \\
&\hspace{0.5cm} +  \int_{0}^{\psi_{k} - \lambda}\lambda\zeta_k(\lambda)g(\phi) d\phi + \int_{\psi_{k-1}}^{2\pi}\lambda\zeta_k(\lambda)g(\phi) d\phi + 
\end{align*}
\begin{align*}
\int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi = &\int_{\tfrac{(2k+1)\pi}{M} - \lambda}^{\tfrac{(2k+1)\pi}{M}}v_k(\phi)g(\phi)d\phi \\
&\hspace{0.5cm}+ \lambda\zeta_k(\lambda) \int_{\tfrac{(2k-1)\pi}{M}}^{\tfrac{(2k+1)\pi}{M}}g(\phi)d\phi.
\end{align*}
Now, since $g(\phi)$ is continuous at $(2k+1)\tfrac{\pi}{M}$ for each integer $k$, and $v_k(\phi)$ is continuous and $v_k(\tfrac{(2k+1)\pi}{M}) =  2\sin(\tfrac{\pi}{M})$,
\begin{align*}
\int_{\tfrac{(2k+1)\pi}{M} - \lambda}^{\tfrac{(2k+1)\pi}{M}}&v_k(\phi)g(\phi)d\phi \\
&= \lambda( v_k(\tfrac{(2k+1)\pi}{M})g(\tfrac{(2k+1)\pi}{M}) + \nu_k(\lambda) ) \\
&= \lambda( 2\sin(\tfrac{\pi}{M})g(\tfrac{(2k+1)\pi}{M}) + \nu_k(\lambda) )
\end{align*}
where $\nu_k(\lambda)$ is function that goes to zero as $\lambda$ goes to zero.  To keep the notation clean put $A_k = \int_{\tfrac{(2k-1)\pi}{M}}^{\tfrac{(2k+1)\pi}{M}}g(\phi)d\phi$.  For each $k\in\ints$, $A_k$ is a nonnegative finite constant less than one.  Now
\begin{align*}
\int_0^{2\pi} v_k(\lambda, \phi) &g(\phi) d\phi \\
&= \lambda( 2\sin(\tfrac{\pi}{M})g(\tfrac{(2k+1)\pi}{M}) + \nu_k(\lambda) + \zeta_k(\lambda) A_k )
\end{align*}
and
\begin{align*}
k_2(\lambda) &= \sum_{k = 0}^{M-1} \lambda( 2\sin(\tfrac{\pi}{M})g(\tfrac{(2k+1)\pi}{M}) + \nu_k(\lambda) + \zeta_k(\lambda) A_k ) \\
 &= \epsilon(\lambda) + 2 \lambda \sin(\tfrac{\pi}{M}) \sum_{k = 0}^M g(\tfrac{(2k+1)\pi}{M})
\end{align*}
where $\epsilon(\lambda) = \sum_{k=0}^M\big( \nu_k(\lambda) + \zeta_k(\lambda) A_k \big)$ is a function that goes to zero as $\lambda$ goes to zero.  Because $\hat{\lambda}_L$ converges almost surely to zero as $L \rightarrow\infty$, then $\epsilon(\hat{\lambda}_L)$ converges almost surely (and therefore also in probability) to zero as $L \rightarrow\infty$, i.e. $\epsilon(\hat{\lambda}_L) = o_P(1)$.  So
\[
k_2(\hat{\lambda}_L) = o_P(1) + 2 \hat{\lambda}_L \sin(\tfrac{\pi}{M}) \sum_{k = 0}^{M-1} g(\tfrac{(2k+1)\pi}{M})
\]
as required.

>>>>

\begin{theorem}\label{thm:normality} (Asymptotic normality)
Under the same conditions as Theorem~\ref{thm:consistency}, let $f(r,\phi)$ be the joint probability density function of $R_1$ and $\Phi_1$, and let
\[
g(\phi) = \int_{0}^{\infty} r f(r,\phi) dr.
\]
Put $\hat{\lambda}_L = \sfracpart{\theta_0 - \hat{\theta}}_\pi$ and $\hat{m}_L = \hat{\rho} - \rho_0 G(0)$. If $g(\phi)$ is continuous at $\phi = (2k+1)\tfrac{\pi}{M}$ for each $k = 0, 1, \dots M-1$, then the distribution of $(\sqrt{L}\lambda_L, \sqrt{L}m_L)$ converges to the bivariate normal with zero mean and covariance
\[
C = \frac{1}{(p + H d)^2} \left( \begin{array}{cc} 
pA_1 + dA_2 & ? \\
? & ?
\end{array} \right)
\]
as $L \rightarrow \infty$, where
\[
H = h_2(0) -  2 \sin(\tfrac{\pi}{M}) \sum_{k = 0}^{M-1} g(\tfrac{2\pi}{M}k + \tfrac{\pi}{M}),
\]
\[
A_1 = \expect R_1^2\sin^2(\Phi_1), \qquad A_2 = \expect R_1^2\sin^2\fracpart{\Phi_1}.
\]
\end{theorem}

@@

\begin{lemma}\label{lem:expRvlamphi}
$W(\lambda) =  \lambda(H_1 + \gamma(\lambda))$ where $\gamma(\lambda)$ is a function that goes to zero as $\lambda$ goes to zero.
\end{lemma}
\begin{IEEEproof}
In this lemma, as Lemma~\ref{lem:k2conv}, we are working under the assumption that that $0 \leq \lambda < \frac{\pi}{M}$.  An analgous argument follows when $-\tfrac{\pi}{M} \leq \lambda < 0$.  Recalling that $f(r,\phi)$ is the joint probability density function of $R_1$ and $\Phi_1$, then,
\begin{align*}
W(\lambda) &= \expect R_1 v(\lambda, \Phi_1) = \int_0^{2\pi}\int_{0}^\infty r v(\lambda, \phi) f(r,\phi) dr d\phi \\
&= \int_0^{2\pi} v(\lambda, \phi) g(\phi) d\phi,
\end{align*}
and, since $v(\lambda, \phi) = \sum_{k\in\ints} v_k(\lambda, \phi)$,
\begin{equation}\label{eq:Winfsum}
W(\lambda) = \sum_{k \in \ints} \int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi.
\end{equation}
Now, when $0 < k < M$, we have $0 < \psi_{k-1} < \psi_k < 2\pi$, so, using~\eqref{eq:vk},
\begin{align*}
\int_0^{2\pi} v_k(\lambda, \phi) &g(\phi) d\phi = \int_{\psi_{k-1}}^{\psi_{k}} v_k(\lambda, \phi) g(\phi) d\phi \\
&= \lambda a_k(\lambda) + \lambda b_k(\lambda) + \lambda c_k(\lambda),
\end{align*}
where, for each integer $k = 1, \dots, M-1$, the functions $a_k$ and $b_k$ are
\begin{equation}\label{eq:ak}
a_k(\lambda) = \int_{\psi_k-\lambda}^{\psi_k}\eta_k(\lambda, \phi) g(\phi) d\phi,
\end{equation}
\[
b_k(\lambda) = \zeta_k(\lambda) \int_{\psi_{k-1}}^{\psi_k -\lambda}g(\phi) d\phi,
\]
and
\begin{equation}\label{eq:ck}
c_k(\lambda) = \frac{1}{\lambda} \int_{\psi_{k} - \lambda}^{\psi_{k}} s_k(\phi) g(\phi) d\phi.
\end{equation}
Observe that $a_k(\lambda)$ and $b_k(\lambda)$ are functions that converge to zero as $\lambda$ goes to zero, whilst $c_k(\lambda)$ converges to 
\[
s_k(\psi_k)g(\psi_k) = -2\sin(\tfrac{\pi}{M}) g(\tfrac{2\pi}{M}k + \tfrac{\pi}{M})
\]
Now, when $k = 0$, we have $\psi_{-1} < 0 < \psi_0 - \lambda < \psi_0 < 2\pi$, so that
\[
\int_0^{2\pi} v_0(\lambda, \phi) g(\phi) d\phi = \lambda a_0(\lambda) + \lambda b_0(\lambda) +  \lambda c_0(\lambda),
\]
where $a_0(\lambda)$ and $c_0(\lambda)$ are defined as in~\eqref{eq:ak}~and~\eqref{eq:ck}, and
\[
b_0(\lambda) = \zeta_0(\lambda) \int_{0}^{\psi_k-\lambda} g(\phi) d\phi.
\]
When $k = M$, we have $0 < \psi_{M-1} < 2\pi < \psi_{M} - \lambda$, so that
\[
\int_0^{2\pi} v_{M}(\lambda, \phi) g(\phi) d\phi = \lambda b_{M}(\lambda)
\]
where 
\[
b_{M}(\lambda) = \zeta_{M}(\lambda) \int_{\psi_{M-1}}^{2\pi}g(\phi) d\phi.
\]
Otherwise, when $k < 0$ or $k > M$, 
\[
\int_0^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi = 0.
\]
So the infinite sum in~\eqref{eq:Winfsum} can be written as the finite sum,
\begin{align*}
W(\lambda) &= \sum_{k=0}^{M} \int_{0}^{2\pi} v_k(\lambda, \phi) g(\phi) d\phi \\
&= \sum_{k=0}^{M-1} \lambda c_k(\lambda) + \sum_{k=0}^{M-1} \lambda a_k(\lambda) + \sum_{k=0}^{M} \lambda b_k(\lambda) \\
&= \lambda \left( C_k(\lambda)  + A_k(\lambda) + B_k(\lambda) \right).
\end{align*}
where 
\[
A_k(\lambda) = \sum_{k=0}^{M-1} a_k(\lambda), \;\;\; B_k(\lambda) = \sum_{k=0}^{M} b_k(\lambda), \;\;\; \text{and},
\]
\[
C_k(\lambda) = \sum_{k=0}^{M-1} c_k(\lambda).
\]
Observe both $A_k(\lambda)$ and $B_k(\lambda)$ converges to zero as as $\lambda$ goes to zero, and $C_k(\lambda)$ converges to $H_1$ as $\lambda$ converges to zero.  Put
\[
\gamma(\lambda) = A_k(\lambda) + B_k(\lambda) + C_k(\lambda) - H_1.
\]
Then $\gamma(\lambda)$ converges to zero as $\lambda$ goes to zero and $W(\lambda) = \lambda(H_1 + \gamma(\lambda))$.  The proof follows.
\end{IEEEproof}
